% 04_capi_fieldwork_post

\section{Fieldwork Operations}

The CAPI baseline was carried out face-to-face using Tablet-Assisted Personal
Interviews on a mobile data-collection platform (SurveyToGo), with the
questionnaire developed by the World Bank in collaboration with the Philippine
Survey and Research Center (PSRC). Data collection ran from September 18 to
October 15, 2025. Each baseline interview lasted approximately two hours, and
the call sheet was also programmed in SurveyToGo with embedded GPS coordinates
to facilitate field monitoring.

Fieldwork achieved its full target: the completed interviews totalled 2,470
households, distributed across the broad areas as NCR (450), North-Central Luzon
(510), South Luzon (530), Visayas (430), and Mindanao (550). A separate pilot
of 12 interviews across four language programs (Tagalog, Cebuano, Hiligaynon,
and Waray) was conducted before the launch of baseline fieldwork to test the
instrument.

The Field Documentation Summary records material operational challenges during
the window. Multiple natural disasters struck between September and October
2025, including Super Typhoon Ragasa (September 22), Typhoon Opong (September
26--30), a magnitude 6.9 earthquake offshore near Cebu City (September 30), and
a magnitude 7.4 earthquake in Manay, Davao Oriental (October 10). These events
disrupted schedules, restricted movement, and limited access to respondents, and
were compounded by interviewer attrition (back-outs mid-fieldwork and illness
during harsh weather). PSRC responded with prompt interviewer replacement,
additional training days, and timeline extensions to secure comprehensive
coverage.

\begin{refbox}
Baseline field documentation:\\
\rd{CATI/Field Reports/L2PHL- Field Documentation Summary (Baseline & CATI R1) v2 17December2025.pdf}
\end{refbox}

\section{Post-Fieldwork Processing}

Raw tablet data is transformed into an analysis-ready sample through a fixed,
ordered pipeline of Stata do-files. Each stage reads the output of the previous
stage and writes a new dataset, so the full path from raw export to weighted
sample is reproducible end to end.

\begin{procbox}{Baseline Processing Pipeline}
\begin{enumerate}
  \item \textbf{Stage 1 --- stg2raw:} the raw survey export is converted to a
        Stata \rd{.dta} file.
  \item \textbf{Stage 2 --- raw2dta:} cleaning, variable renaming, labeling, and
        consistency corrections are applied.
  \item \textbf{Stage 3 --- psu2wgt:} sampling weights are constructed.
  \item \textbf{Stage 4 --- dta2smp:} the analysis sample is assembled.
\end{enumerate}
\end{procbox}

Raw data is never modified in place; every cleaning step runs through a Stata
do-file so that each transformation can be audited and re-run.

\begin{refbox}
Round00 pipeline do-files:\\
\rd{CAPI/Round00/do/}\\
\rd{CAPI/Round00/do/1_L2PHL_CAPI_R00_stg2raw@AP@20260407.do}\\
\rd{CAPI/Round00/do/2_L2PHL_CAPI_R00_raw2dta@AP@20260407.do}\\
\rd{CAPI/Round00/do/3_L2PHL_CAPI_R00_psu2wgt@AP@20260407.do}\\
\rd{CAPI/Round00/do/4_L2PHL_CAPI_R00_dta2smp@AP@20260407.do}
\end{refbox}
