% 06_cati_design_quest
\parttitle{Part III: High-Frequency Panel Survey (CATI)}

The high-frequency panel is the follow-up phase of the survey. Where the baseline
provides a single, once-off portrait of the population, the CATI panel is a monthly
telephone survey of the baseline households that tracks fast-moving conditions in the
months between rounds. It trades the breadth and depth of the face-to-face baseline for
frequency, allowing the programme to monitor how households experience shocks, income
changes, and food security as they unfold rather than only at a single point in time.

\section{Panel Design}

The CATI sample follows the baseline households by phone. Rounds R1 through R9 run
monthly from November 2025 to July 2026, giving a rolling monthly reading on the same
population that the baseline measured once.

The panel is an \emph{attrition-plus-replenishment} design; it is not a closed cohort.
Households drop out across rounds as phone numbers go stale or respondents decline, and
new households enter to keep the achieved sample near target. The round-to-round sample
is therefore a mix of stayers (households present in consecutive rounds), leavers
(households that drop out), and new entrants (households added in later rounds). Any
round-over-round comparison must account for this composition rather than assume the same
households throughout.

The pooled, harmonized masters that the analysis and quality-control pipeline read live
in the high-frequency working directory. Two spine files carry the survey weights, and one
pooled file per module carries the harmonized responses across all rounds.

\begin{refbox}
Panel spine masters (person-round and household-round):\\
\rd{CATI/Analysis/HF/l2phl_cati_individual.dta} (holds the individual weight)\\
\rd{CATI/Analysis/HF/l2phl_cati_household.dta} (holds household and population weights)\\[4pt]
Per-module pooled masters (M00--M09):\\
\rd{CATI/Analysis/HF/l2phl_M00_passport.dta}\\
\rd{CATI/Analysis/HF/l2phl_M01_roster.dta}\\
\rd{CATI/Analysis/HF/l2phl_M02_education.dta}\\
\rd{CATI/Analysis/HF/l2phl_M03_shock.dta}\\
\rd{CATI/Analysis/HF/l2phl_M04_employment.dta}\\
\rd{CATI/Analysis/HF/l2phl_M05_income.dta}\\
\rd{CATI/Analysis/HF/l2phl_M06_finance.dta}\\
\rd{CATI/Analysis/HF/l2phl_M07_health.dta}\\
\rd{CATI/Analysis/HF/l2phl_M08_food_nonfood.dta}\\
\rd{CATI/Analysis/HF/l2phl_M09_views.dta}
\end{refbox}

\section{Questionnaire and Round-Specific Modules}

The CATI instrument has ten modules. It reuses the baseline module structure but is
shorter, since a telephone interview cannot carry the full baseline battery.

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Module} & \textbf{Name} \\
\midrule
M00 & Passport \\
M01 & Roster \\
M02 & Education \\
M03 & Shocks \\
M04 & Employment \\
M05 & Income \\
M06 & Finance \\
M07 & Health \\
M08 & Food / FIES \\
M09 & Views \\
\bottomrule
\end{tabular}
\end{center}

Some blocks are round-specific or rotating rather than fixed across all rounds. The health
module (M07) carries only a short set of items in most rounds but has a full expansion in
Rounds 5 and 8. A Middle-East situation block appears within the Views module (M09) in
Rounds 6 through 8. Finance bank and mobile-money gate questions are introduced from Round
5 onward. Because of this evolution, the per-round Kobo XLSForms are the ground truth for
exactly which questions exist in each round, and any analysis of a single variable should
confirm its presence round by round against the relevant form.

\begin{sloppypar}
\begin{refbox}
Per-round Kobo XLSForms (ground truth for round-specific content), in \rd{CATI/KOBO/}:\\
\rd{CATI/KOBO/L2PHL_CATI_R01.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R02.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R03.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R04.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R05.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R06.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R07.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R08.xlsx}\\
\rd{CATI/KOBO/L2PHL_CATI_R09.xlsx}
\end{refbox}
\end{sloppypar}
