% 07_cati_processing_weighting

\section{Per-Round Processing}

Each round is processed from its raw Kobo export through a round-specific do-file and then
pooled into the harmonized high-frequency masters that the analysis and quality-control
pipeline read. The round do-file cleans and standardizes that round's delivery; the pooling
step stacks the cleaned rounds into one file per module, keyed by round and household, so that
every downstream analysis reads a single harmonized panel rather than nine separate deliveries.

When the firm delivers revised round data, the masters are re-pooled rather than merely
appended. The pooling step rebuilds the harmonized files across all rounds from the current
round deliveries, so a late correction to an earlier round is reflected in the masters instead
of being lost behind an already-frozen pool. This is why a revised delivery can change values
in earlier rounds and not only add the newest round.

\section{Weighting}

The panel weights are recomputed each round rather than carried forward unchanged, because the
achieved sample changes composition from round to round. The construction proceeds in three
steps, summarized here; the full derivation is in the weighting technical note cited below.

The individual weight is recalibrated each round to census population cells defined by age
group $\times$ sex $\times$ stratum. It starts from a baseline individual weight and is scaled
within each cell so that the sum of individual weights in the cell matches the census population
total for that cell in that round. The result is the per-round individual weight \rd{indw}.

The population weight for a household is the sum of the individual weights of its members. The
household weight is the mean individual weight within the household; it is then smoothed at the
primary-sampling-unit level (replaced by the PSU mean) and rescaled so that household totals
match census household totals per stratum. These give \rd{popw} and \rd{hhw} on the
household-level file.

\begin{refbox}
Full derivation of the panel weights:\\
\rd{CAPI/Analysis/SL/tex/L2PHL_WEIGHTING_TECHNICAL_NOTE.pdf}
\end{refbox}

\subsection{The target\_hh\_imputed.dta file}

A recurring firm-turnover question is what \rd{target_hh_imputed.dta} is and whether it is part
of the weight construction. It is not. This file is the survey-to-survey (S2S) income-imputation
product described in Part~II (Income Imputation); it is not produced by the weighting code.

\begin{sloppypar}
The file is created under \rd{CAPI/S2S/target_hh_imputed.dta} and copied to
\rd{CATI/Analysis/HF/R00/target_hh_imputed.dta}. In the CATI analysis do-file it is merged onto
the baseline weight file by household id: an \rd{m:1} merge on \rd{hhid} that keeps the single
variable \rd{pcinc_imp_mean} (labeled ``PC HH imputed income''), with \rd{assert(3)} requiring a
full match on both sides. The merge attaches a per-capita imputed household income to each
household.
\end{sloppypar}

The purpose is to enable income-quintile and welfare breakdowns of the panel indicators.
\rd{pcinc_imp_mean} is an imputed-welfare input, not a component of the survey weights. This is
why it appears in the analysis do-file but not in the earlier weighting do-file: it is joined to
the already-weighted file, not used to build the weights.

\begin{sloppypar}
\begin{refbox}
The merge (analysis do-file) and the baseline weight file it merges onto:\\
\rd{CATI/Analysis/do/hf_l2phl_analysis@AP@20260709.do}\\
\rd{CATI/Analysis/HF/R00/final_weights.dta}\\[4pt]
The imputation method (S2S note):\\
\rd{CAPI/S2S/S2S_PHL_note.docx}
\end{refbox}
\end{sloppypar}
