% 08_qc_architecture

\parttitle{Part IV: Quality Control and the DQ Dashboard}

Quality control is the live, hand-over-critical workstream of the panel. Each
round the firm delivers new data, and the survey team must confirm that the
delivery holds together before any indicator is trusted. The data-quality (DQ)
dashboard is the instrument for that confirmation: it is regenerated from the
pooled masters by a single command, so the checks never drift from the code.
This part documents how to run the pipeline, how to read the panels it
produces, how to maintain it as rounds and questionnaires change, and why its
outputs can be trusted.

\section{Pipeline Architecture}

\begin{sloppypar}
One entry point regenerates everything. The pipeline script
\rd{CATI/Analysis/QC/update_pipeline.py}, run as \verb|python3 update_pipeline.py --all|,
reads the pooled high-frequency masters, runs the check and build scripts in
order, writes intermediate JSON to \rd{CATI/Analysis/QC/cache/}, and produces
the HTML dashboard and the Excel cross-round report. Because the checks read a
round column in the pooled data, adding a round requires only a few round-count
constant edits and registering the new questionnaire form, not changes to the
check logic; the step-by-step procedure is in the maintenance playbook.
\end{sloppypar}

\begin{procbox}{Full pipeline run}
\begin{enumerate}
  \item \textbf{Detect files:} scan \rd{CATI/Analysis/HF/} for pooled and per-round
        \rd{.dta} masters, \rd{CATI/Questionnaire/} for questionnaire Excel
        files, and \rd{CATI/Round*/do/} for processing do-files.
  \item \textbf{Build DQ data (\rd{build_dq.py}):} run the data-quality checks
        on the pooled masters and write \rd{CATI/Analysis/QC/cache/dq_data.json}.
  \item \textbf{Build panel tracker (\rd{build_panel.py}):} compute per-round
        household participation and attrition into \rd{CATI/Analysis/QC/cache/panel_data.json}.
  \item \textbf{Build interviewer performance (\rd{build_interviewer.py}):}
        summarize operator performance into \rd{CATI/Analysis/QC/cache/interviewer_data.json}.
  \item \textbf{Parse questionnaires and Kobo skip logic (\rd{parse_kobo.py}):}
        extract the cross-round question tables and the Kobo relevant/skip
        rules per variable into \rd{CATI/Analysis/QC/cache/kobo_skip_logic.json}.
  \item \textbf{Build issue intelligence (\rd{build_issues.py}):} assemble the
        tracked data-quality issues into \rd{CATI/Analysis/QC/cache/issues.json}.
  \item \textbf{Render dashboard (\rd{gen_dashboard.py}):} read the cache and
        write \rd{CATI/Analysis/QC/output/l2phl_dq_dashboard.html}.
  \item \textbf{Build Excel report (\rd{build_report.py}):} write the
        cross-round questionnaire comparison to
        \rd{CATI/Analysis/QC/output/L2PHL_Questionnaire_Cross_Round_Report.xlsx}.
\end{enumerate}
Single command: \verb|python3 update_pipeline.py --all|
\end{procbox}

The seven build and check scripts each own one stage of the run:

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Script} & \textbf{Role} \\
\midrule
\rd{build_dq.py}          & Runs the data-quality checks on the pooled masters. \\
\rd{build_panel.py}       & Builds the household participation and attrition tracker. \\
\rd{build_interviewer.py} & Summarizes interviewer/operator performance. \\
\rd{parse_kobo.py}        & Extracts skip logic from the Kobo XLSForms. \\
\rd{build_issues.py}      & Assembles the tracked data-quality issues. \\
\rd{gen_dashboard.py}     & Renders the HTML dashboard from the cache. \\
\rd{build_report.py}      & Builds the Excel cross-round questionnaire report. \\
\bottomrule
\end{tabular}
\end{table}

\begin{refbox}
Pipeline entry point and scripts:\\
\rd{CATI/Analysis/QC/update_pipeline.py}\\
\rd{CATI/Analysis/QC/scripts/}\\[4pt]
Generated outputs:\\
\rd{CATI/Analysis/QC/output/l2phl_dq_dashboard.html}\\
\rd{CATI/Analysis/QC/output/L2PHL_Questionnaire_Cross_Round_Report.xlsx}
\end{refbox}

\section{Dashboard Panels}

The dashboard collects, in one page, the panels a reviewer needs to judge a
delivery:

\begin{itemize}
  \item \textbf{Completion tracker:} per-round household participation, showing
        how many baseline households answered each round.
  \item \textbf{Data-quality heatmap:} per-module red/amber/green cells by
        variable, flagging skip-logic violations, missing mandatory fields, and
        out-of-range values.
  \item \textbf{Kobo skip-logic panel:} the relevant/skip rules parsed from the
        XLSForms for each variable, so a flagged cell can be checked against the
        rule that should govern it.
  \item \textbf{Issue intelligence:} the tracked data-quality issues, with their
        classification and status.
  \item \textbf{Interviewer performance:} operator-level summaries of throughput
        and quality.
  \item \textbf{Cross-round questionnaire report:} which variables are present in
        each round, with new, dropped, and changed questions surfaced across the
        panel.
\end{itemize}
