% 11_annex_a

\parttitle{Annex A: Replicability Package}

This annex lists the key scripts and folders by workflow stage. All paths are
relative to the repository root. Running each stage in sequence reproduces the
processing, weights, quality control, and deliverables of the survey: the
baseline (CAPI) pipeline, the per-round panel (CATI) processing, the quality
control pipeline, and the storyline, dashboard, and deep-dive products.

\section{Replication by Stage}

\subsection{Baseline (CAPI)}

The baseline is processed by four numbered do-files in \rd{CAPI/Round00/do/},
run in order. Each stage reads the output of the prior stage; inputs only ever
flow forward.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}llp{6.2cm}@{}}
\toprule
\textbf{Stage} & \textbf{Script} & \textbf{Purpose} \\
\midrule
1 & \rd{1_L2PHL_CAPI_R00_stg2raw@AP@20260407.do} &
    Assemble the field-server staging exports into a raw dataset. \\
2 & \rd{2_L2PHL_CAPI_R00_raw2dta@AP@20260407.do} &
    Clean and label the raw data into module datasets. \\
3 & \rd{3_L2PHL_CAPI_R00_psu2wgt@AP@20260407.do} &
    Build the sampling design and compute the survey weights (indw, hhw). \\
4 & \rd{4_L2PHL_CAPI_R00_dta2smp@AP@20260407.do} &
    Produce the analysis-ready sample datasets. \\
\bottomrule
\end{tabular}
\end{table}

The Survey-to-Survey (S2S) income imputation is a separate baseline product; its
scripts and datasets live in \rd{CAPI/S2S/} and link imputed income to the
baseline records for the income-quintile and region breakdowns.

\subsection{Panel (CATI) --- Per-Round Processing}

Each round is processed in its own round folder, one per delivery, from
\rd{CATI/Round01/} through \rd{CATI/Round09/}. A round folder holds that
round's raw delivery, processing do-file, and fixes. The processed rounds are
then pooled into the high-frequency masters and analyzed centrally.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lp{7.2cm}@{}}
\toprule
\textbf{Folder} & \textbf{Contents} \\
\midrule
\rd{CATI/Round01/} \ldots \rd{CATI/Round09/} &
    Per-round processing: raw delivery, round do-file, and fixes. \\
\rd{CATI/Analysis/HF/} &
    Pooled high-frequency panel masters (individual and household), rebuilt when
    a round is added or re-pooled. \\
\rd{CATI/Analysis/do/} &
    Central panel analysis do-file
    (\rd{hf_l2phl_analysis@AP@20260709.do}) run over the pooled masters. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Quality Control Pipeline}

\begin{sloppypar}
One entry point regenerates the data-quality outputs. The orchestrator
\rd{CATI/Analysis/QC/update_pipeline.py} runs the build and check scripts in
\rd{CATI/Analysis/QC/scripts/} against the pooled masters and writes the
dashboard and cross-round report to \rd{CATI/Analysis/QC/output/}.
\end{sloppypar}

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Script} & \textbf{Role} \\
\midrule
\rd{build_dq.py}          & Runs the data-quality checks on the pooled masters. \\
\rd{build_panel.py}       & Builds the household participation and attrition tracker. \\
\rd{build_interviewer.py} & Summarizes interviewer/operator performance. \\
\rd{parse_kobo.py}        & Extracts skip logic from the Kobo XLSForms. \\
\rd{build_issues.py}      & Assembles the tracked data-quality issues. \\
\rd{gen_dashboard.py}     & Renders the HTML dashboard from the cache. \\
\rd{build_report.py}      & Builds the Excel cross-round questionnaire report. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Storylines, Dashboards, and Deep Dives}

The analytical products read the finished datasets and present the results. The
baseline dashboard is built in \rd{CAPI/Analysis/DB/}, the baseline storyline in
\rd{CAPI/Analysis/SL/}, and the ten thematic deep dives in
\rd{CAPI/Analysis/DD/}. The panel storyline is built under
\rd{CATI/Analysis/SL/}. Each folder holds the do-files or code, results, and the
self-contained HTML deliverable for its product.

\begin{refbox}
Deliverable workstreams:\\
\rd{CAPI/Analysis/DB/} --- baseline dashboard\\
\rd{CAPI/Analysis/SL/} --- baseline storyline\\
\rd{CAPI/Analysis/DD/} --- ten thematic deep dives\\
\rd{CATI/Analysis/SL/} --- panel storyline
\end{refbox}

\section{Key Conventions}

The pipeline follows a small set of conventions so that any stage can be located
and re-run without ambiguity:

\begin{itemize}
  \item \textbf{Date-stamped folders and files:} working outputs carry a
        \verb|YYYYMMDD| stamp, so the version used in a run is unambiguous.
  \item \textbf{\rd{@AP@} do-file naming, one live file per slot:} each logical
        role has exactly one live file, the latest-dated \verb|@AP@| version;
        superseded files move to a local \rd{_attic/} folder.
  \item \textbf{Three-stage flow:} raw $\rightarrow$ cleaned/weighted
        $\rightarrow$ analysis. Inputs only ever flow forward; a later stage
        never writes back to an earlier one.
  \item \textbf{Forward-slash paths:} all paths are written with forward slashes,
        relative to the repository root, so they resolve on any platform.
  \item \textbf{Raw data never modified in place:} raw snapshots are preserved
        for audit; cleaning and fixes are applied downstream, never to the raw
        delivery.
\end{itemize}
