% 12_annex_b

\parttitle{Annex B: Turnover Questions --- Answered}

This annex answers, in the firm's own grouping, each question raised for the
turnover meeting, with a short answer and a pointer to the section that covers
it in full.

\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{longtable}{>{\raggedright\arraybackslash}p{5.1cm} >{\raggedright\arraybackslash}p{7.4cm} >{\raggedright\arraybackslash}p{2.2cm}}
\toprule
\textbf{Question} & \textbf{Short answer} & \textbf{See} \\
\midrule
\endhead
\multicolumn{3}{@{}l}{\textbf{Quality Checks}} \\
Will we keep access to the QC Flags Dashboard after turnover? &
The dashboard is a self-contained HTML regenerated from the repository pipeline;
the receiving team runs and owns it going forward, with no external dependency. &
Part IV; Annex C \\[0.4em]
Will our team own creating and maintaining the QC dashboard? Please walk us
through it. &
Yes. The full generate-and-maintain process --- architecture, the one-command
run, and the maintenance playbook --- is documented in Part IV. &
Part IV \\[0.4em]
\midrule
\multicolumn{3}{@{}l}{\textbf{Data Processing --- Weighting}} \\
Where does \texttt{target\_hh\_imputed.dta} come from, and what is its purpose
in weighting? &
It is the survey-to-survey (S2S) income-imputation product (per-capita imputed
income), copied to the high-frequency R00 folder and merged onto the baseline
weight file by household id for income-quintile breakdowns; it is not a
component of weight construction. &
Part II (Income Imputation); Part III (Weighting) \\[0.4em]
\midrule
\multicolumn{3}{@{}l}{\textbf{Dashboard}} \\
What edits are needed when a new round of data is uploaded, and how do they
reach the dashboard? &
Bump the round-count constant in four build scripts, register the round's Kobo
form in \texttt{parse\_kobo} and \texttt{update\_pipeline}, then run the
pipeline; the worked Round~9 example is in the playbook. &
Part IV (Playbook) \\[0.4em]
For rounds with new or removed questions, what edits are needed? &
Update the module's authoritative variable list and heatmap in
\texttt{build\_dq} and the standardization in \texttt{gen\_dashboard}; the Kobo
form is the ground truth for what exists in a round. &
Part IV (Playbook) \\[0.4em]
How can we efficiently update dashboard filters when questionnaire logic
changes? &
Register the new Kobo form; \texttt{parse\_kobo} folds each variable's enclosing
relevant condition into the variable automatically, so the skip-logic panel and
gated checks update on re-run. &
Part IV (Playbook) \\[0.4em]
What is the full process from data preparation to final dashboard output? &
A single command, \texttt{update\_pipeline.py -{}-all}, runs the ordered
pipeline from the pooled data to the HTML dashboard and the Excel cross-round
report. &
Part IV (Architecture) \\[0.4em]
\midrule
\multicolumn{3}{@{}l}{\textbf{Other}} \\
How can we trace a number on the dashboard back to the source data? &
Follow the chain do-file to Stata log to Excel to HTML; on the dashboard, trace
the panel value through the cache JSON to the check in \texttt{build\_dq} and
the underlying .dta variable. A cross-checker helper automates this. &
Part IV (Verifying) \\[0.4em]
How can we verify a flag is a real issue and not just a filtering-condition
problem? &
Checks are gated by the Kobo relevant condition; compare any surprising flag
against the skip logic and preload gating first, using the issue-classification
categories. &
Part IV (Verifying) \\[0.4em]
Can the dashboard monitor fieldwork progress and data quality in real time? &
Yes; re-running the pipeline on the latest masters refreshes completion counts
and flags mid-round, so it doubles as a live fieldwork monitor. &
Part IV (Verifying) \\[0.4em]
Which files should we modify most often? &
\texttt{build\_dq.py} (checks), \texttt{gen\_dashboard.py} (rendering),
\texttt{parse\_kobo.py} (skip logic), and \texttt{update\_pipeline.py} (round
registration). &
Part IV (Conventions) \\[0.4em]
Are there coding standards or naming conventions we should follow? &
Yes --- the \texttt{@AP@} do-file naming with one live file per slot,
superseded files archived to \texttt{\_attic}, and forward-slash paths. &
Part IV (Conventions); Annex A \\[0.4em]
What are the most common causes of incorrect flags or counts, and the most
frequent dashboard issues? &
Cross-module variables absent from the pooled data, preload-gated variables,
module items introduced mid-panel, renamed or derived variables, and partial
in-progress rounds read as attrition. &
Part IV (Verifying) \\
\bottomrule
\end{longtable}
\normalsize
